### 2020-09-08 LaTeX/sections/paper.tex
Edits on the figure references - Added the cost in eth and USD (conversions included)
Preliminaries - to be completed

* transparency, front-running
* slow but is becoming more efficient over time, expensive
* Gas model: gas limit, how much, per transaction vs per block, Solidity/EVM quirks: gas refunds

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

@@

>>>>

% transparency, front-running:
\item \textbf{Transparency and Front-running.} Blockchains (in general)  are transparent --- transactions are first relay around the network before being selected by a miner, validated, and included in a block. This allows malicious nodes/miners observe and front-run the transactions by dropping them or attempting to insert their own transactions before the observed transactions~\cite{eskandari2019sok}. In context of a decentralized exchange, front-running attacks enable the malicious nodes to have their orders executed before others and benefit from it.

% slow but is becoming more efficient over time, expensive
\item \textbf{Speed.} Blockchains are not fast architectures --- speed is one of the factors that diminishes the real world potential of blockchains. Blockchains are slow-moving as it takes block interval (\ie time it takes to mine a block) for transactions to be confirmed and included in valid blocks. So it is difficult to push a stock market on the blockchain as stock markets move extremely fast. High-frequency trading (HFT) is a trading method example that uses active computers to process a large number of trades in fractions of a second.  Currently in Ethereum 1.0 blocks are produced at intervals every 10 to19 seconds, note that this is not yet suitable for time sensitive transactions. However, capabilities of blockchains will be further enhanced ad they will become more efficient over time; Ethereum 2.0 has a shorter block time of 12 seconds.

% Gas model: gas limit, how much, per transaction vs per block, Solidity/EVM quirks: gas refunds
\item \textbf{Gas Parameter in Ethereum Transactions.}

Gas is the Ethereum's pseudo-currency and a key variable for the execution of smart contracts. DApps written in high-level programming languages are compiled and translated into a compact representation (called ‘bytecode’) to be further executed on the Ethereum virtual machine or EVM. Each of these opcodes has a fixed amount of gas assigned and is a measure of computational effort. Separating ether from gas prevents transactions cost from being too expensive as they are less impacted by ETH price fluctuations. Gas unit does not a have a monetary value and as mentioned it only  measures the computational work undertaken by miners. To pay miners, Ethereum introduces a \texttt{gas price} --- small denomination of ether called \textbf{Gwei} attached to each gas unit. Essentially, gas price indicates how much users are willing to pay per unit of gas, clearly the higher gas price leads to the faster execution of a transaction. Miners also need to know the total amount of computational work a user is requesting, called the \texttt{gas limit}. \texttt{Gas limit} is a parameter that limits the amount of gas users would spend in a transaction. It protects users from spending unlimited ETH on their transactions and must be set carefully. If the \texttt{gas limit} is too low, the transaction will exceed the limit, all changes will be reversed but the users must still pay for the computational work performed by the miner.

gas is what makes ethereum furnctiom,  it safegaurds the network from overload and incentivises people too keep ethereum running. By seperating eth from gas, txs cost are less influneced by chning price of Eth so keeping txs from being too expensive

gas price: how much you pay per gas unit
gas limit: how much work you are requesting

gas cost (Ether) = gasPrice * gasCost(gas)

gas limit: is a parameter that limits the amount of gas you spend in a transaction (how to estimate? using estimateGas)
gas price how to estimate: using ethgassation 
by defaluth the gas minimum gas limit for ethereum txs is 21000 gas

a block also has a gas limit field, it defines a maximum amount of gas all txs in th eblock combined are allowed to consume. this block gas limit determines the maximum number of transactions within the block. this block gas limt is not fixed and set by miners

* Gas model: gas limit, how much, per transaction vs per block, Solidity/EVM quirks: gas refunds

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
%  = = = = = = Table 2 (dequeue) Conversions = = = = = = %
%
%As of July 2020,  $1 gas = 56\times10^{-9} ether$\footnote{https://ethstats.net/} and 1 ether = \$238.33\footnote{https://coinmarketcap.com/}.
%
%$Transaction cost (eth) = GasUsed (unit) \times Gas Price (eth)$ 
%
%%  = = = = = = Transaction Costs in eth = = = = = = %
%
%Heap with Dynamic Array:    		$2,518,131 \times 56\times10^{-9} = 141,015,336\times 10^{-9}$
%Heap with Dynamic Array:     		$1,385,307 \times 56\times10^{-9} = 77,577,192\times 10^{-9}$
%Heap with Mapping:              		$2,781,684 \times 56\times10^{-9} = 155,774,304\times 10^{-9}$
%Linked List:						$557,085 \times 56\times10^{-9} = 	31,196,760\times 10^{-9}$
%Linked List with Mapping:			$731,514 \times 56\times10^{-9} = 	40,964,784\times 10^{-9}$
%
%%  = = = = = = Transaction Costs in USD = = = = = = %
%
%Heap with Dynamic Array:    		$141,015,336\times 10^{-9} \times 238.33 = \$33.60$
%Heap with Dynamic Array:     		$77,577,192\times 10^{-9} \times 238.33 = \$18.48$
%Heap with Mapping:              		$155,774,304\times 10^{-9} \times 238.33 = \$37.12$
%Linked List:						$31,196,760\times 10^{-9} \times 238.33 = \$7.43$
%Linked List with Mapping:			$40,964,784\times 10^{-9} \times 238.33 = \$9.76$
%
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

@@

%---------+++++++++++++++++++-----------------
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

%  = = = = = = Table 3 (cleaning.tex) Conversions = = = = = = %

%As of July 2020,  $1 gas = 56\times10^{-9} ether$\footnote{https://ethstats.net/} and 1 ether = \$238.33\footnote{https://coinmarketcap.com/}.
%
%$Transaction cost (eth) = GasUsed (unit) \times Gas Price (eth)$ 
%
%%  = = = = = = Transaction Costs in eth = = = = = = %
%
%Linked List with \texttt{SELFDESTRUCT}:     				$557,085 \times 56\times10^{-9} =  31,196,760\times 10^{-9}$  
%Linked List w/o \texttt{SELFDESTRUCT}:     				$721,370 \times 56\times10^{-9} =  40,396,720\times 10^{-9}$ 
%Linked List with Mapping and \texttt{DELETE}:    			$731,514 \times 56\times10^{-9} =  40,964,784\times 10^{-9}$ 
%Linked List with Mapping and w/o \texttt{DELETE}: 		$334,689 \times 56\times10^{-9} =  18,742,584\times 10^{-9}$ 
%
%%  = = = = = = Transaction Costs in USD = = = = = = %
%
%Linked List with \texttt{SELFDESTRUCT}:     				$31,196,760\times 10^{-9}  \times 238.33 = \$7.43$
%Linked List w/o \texttt{SELFDESTRUCT}:     				$40,396,720\times 10^{-9} \times 238.33 = \$9.62$
%Linked List with Mapping and \texttt{DELETE}:    			$40,964,784\times 10^{-9}  \times 238.33 = \$9.76$
%Linked List with Mapping and w/o \texttt{DELETE}: 		$18,742,584\times 10^{-9} \times 238.33 = \$4.46$
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
